% Main Manuscript File - EES Submission
% Spectral Bath Engineering for Quantum-Enhanced Agrivoltaics

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsfonts,graphicx,booktabs,bm,multirow,siunitx,physics}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{rsc}
\usepackage[margin=2.cm]{geometry}

% Hyperref setup
\hypersetup{
    pdftitle={Spectral Bath Engineering for Quantum-Enhanced Agrivoltaics - Main Manuscript},
    pdfauthor={Teguia et al.},
    pdfsubject={Quantum Photosynthesis, Agrivoltaics, Non-Markovian Dynamics},
    pdfkeywords={agrivoltaics, quantum photosynthesis, spectral engineering, non-Markovian dynamics, renewable energy},
    colorlinks=true,
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue
}

\DeclareSIUnit{\yr}{yr}
\DeclareSIUnit{\tonne}{t}
\DeclareSIUnit{\hectare}{ha}
\DeclareSIUnit{\kWh}{kWh}

%=============================================================================
% TITLE AND AUTHORS
%=============================================================================

\title{\textbf{Spectral Bath Engineering for Quantum-Enhanced Agrivoltaics: Advancing Efficiency and Environmental Sustainability via Non-Markovian Dynamics}}

\author{
    Steve Cabrel Teguia Kouam$^{2,*}$,
    Theodore Goumai Vedekoi$^{1}$, 
    Jean-Pierre Tchapet Njafa$^{1}$, \\
    Jean-Pierre Nguenang$^{2}$,
    Serge Guy Nana Engo$^{1}$ \\
    \\
    $^{1}$Department of Physics, Faculty of Science, University of Yaoundé I, Cameroon \\
    $^{2}$Department of Physics, Faculty of Science, University of Douala, Cameroon \\
    \\
    $^{*}$Corresponding author: \texttt{steve.teguia@univ-douala.cm}
}

\date{\today}

%=============================================================================
% DOCUMENT BEGIN
%=============================================================================

\begin{document}

\maketitle

%=============================================================================
% ABSTRACT
%=============================================================================

\begin{abstract}
As global demand for food and clean energy intensifies, agrivoltaic systems have emerged as a vital solution for land-use optimization. However, current designs overwhelmingly treat incident light as a classical photon flux, overlooking the quantum mechanical nature of photosynthetic energy transfer. We introduce \textit{spectral bath engineering}---the strategic spectral filtering of sunlight through semi-transparent organic photovoltaic (OPV) panels to exploit non-Markovian quantum coherence in biological light-harvesting. Using Process Tensor HOPS (PT-HOPS) and Spectrally Bundled Dissipators (SBD) to simulate the Fenna-Matthews-Olsen complex, we demonstrate that selective filtering at vibronic resonance wavelengths (\SIlist{750;820}{\nano\meter}) enhances the electron transport rate (ETR) by \SI{25}{\percent} relative to standard Markovian models. This quantum advantage is driven by vibronic resonance-assisted transport, which extends coherence lifetimes by \SIrange{20}{50}{\percent} and nearly doubles pairwise concurrence (\SI{+89}{\percent}). Multi-objective Pareto optimization identifies OPV configurations reaching \SI{18.8}{\percent} power conversion efficiency while sustaining an \SI{80.5}{\percent} system ETR, potentially generating an additional USD~\numrange{470}{3000}\,\si{ha^{-1}\,yr^{-1}} in revenue. Environmental simulations across nine climate zones, including sub-Saharan Africa, confirm persistent ETR enhancements of \SIrange{18}{24}{\percent}. Finally, eco-design analysis using quantum reactivity descriptors ensures that these technological gains are achieved using sustainable, biodegradable materials. By bridging quantum biology and renewable energy engineering, this work provides a quantitative blueprint for next-generation agrivoltaic materials that co-optimize agricultural productivity and energy yield.
\end{abstract}

%=============================================================================
% BROADER CONTEXT
%=============================================================================
\noindent\textbf{Broader context}

The escalating global need for food and clean energy necessitates innovative land-use strategies that move beyond simple co-location. Agrivoltaic systems represent this frontier, yet current implementations neglect the molecular-scale biological processes governing light harvesting. In photosynthetic complexes, energy transfer efficiency is deeply influenced by the spectral composition of incident light and nascent quantum mechanical effects. In this study, we demonstrate that engineering the transmission spectrum of semi-transparent solar panels to target specific vibronic resonances can significantly enhance biological energy transfer. This "spectral bath engineering" approach effectively bridges quantum biology with renewable energy engineering, offering design rules for next-generation materials that improve both crop productivity and solar yields. Furthermore, our integration of eco-design analysis ensures that these quantum-enhanced benefits do not come at an environmental cost, utilizing sustainable OPV chemistries and exhibiting exceptional operational stability. This work provides a scalable pathway for achieving several UN Sustainable Development Goals, particularly in regions where food and energy security are most under pressure.

\vspace{1em}

%=============================================================================
% KEYWORDS
%=============================================================================

\noindent\textbf{Keywords:} Agrivoltaics, Quantum photosynthesis, Spectral engineering, Non-Markovian dynamics, Renewable energy, Organic photovoltaics, Coherence-assisted transport, Sustainable agriculture

%=============================================================================
% MAIN CONTENT (MODULAR SECTIONS)
%=============================================================================

\input{files2/introduction}

\input{files2/theory_methods}

\input{files2/results}

\input{files2/discussion}

\input{files2/conclusion}

%=============================================================================
% ACKNOWLEDGMENTS
%=============================================================================

\section*{Acknowledgments}

This work was supported by the University of Yaoundé I and the University of Douala.

%=============================================================================
% DATA AVAILABILITY
%=============================================================================

\section*{Data availability statement}

All data supporting the findings of this study are available within the article and its Supporting Information. Raw simulation output files, analysis scripts, and parameter sets are available from the corresponding author upon reasonable request. Our custom PT-HOPS/SBD simulation framework, computational notebooks, source code, and datasets generated during this study are available in the GitHub repository at \url{https://github.com/NanaEngo/Quantum_Agrivoltaic_HOPS}. Reproducibility information: All simulations were performed using Python 3.12.12, NumPy 2.0.2, and SciPy 1.14.1. Computational parameters and environment configurations are documented in the Supporting Information. All reported values include standard errors calculated from ensemble averaging, with 95\% confidence intervals explicitly stated for all quantitative results derived from 100 independent realizations.

%=============================================================================
% CONFLICTS OF INTEREST
%=============================================================================

\section*{Conflicts of Interest}

The authors declare no conflicts of interest.

%=============================================================================
% AUTHOR CONTRIBUTIONS
%=============================================================================

\section*{Author Contributions}

\textbf{Steve Cabrel Teguia Kouam}: Methodology, Validation, Formal analysis, Writing -- original draft. \textbf{Theodore Goumai Vedekoi}: Software, Investigation, Data curation, Writing -- original draft. \textbf{Jean-Pierre Tchapet Njafa}: Conceptualization, Theoretical framework, Writing -- review \& editing. \textbf{Jean-Pierre Nguenang}: Resources, Supervision, Formal analysis. \textbf{Serge Guy Nana Engo}: Project administration, Conceptualization, Theoretical framework, final Manuscript editing. All authors have given approval to the final version of the manuscript.

%=============================================================================
% REFERENCES
%=============================================================================

\bibliographystyle{rsc}  % RSC house style (numbered, natbib-compatible)
\bibliography{references}  % BibTeX file with all references

%=============================================================================
% SUPPORTING INFORMATION
%=============================================================================

\section*{Supporting Information}

Supporting Information includes detailed environmental factor models, biodegradability assessment, extended validation data (12 tests), complete FMO parameter sets, computational performance benchmarks, and supplementary figures S1--S8.

%=============================================================================
\end{document}
%=============================================================================