% Main manuscript file - AEM submission

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsfonts,graphicx,booktabs,chemformula,multirow,siunitx,physics}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage[margin=2.5cm]{geometry}
\usepackage{xr}
\externaldocument{Supporting_Info_AEM}
% Hyperref setup
\hypersetup{
    pdftitle={Molecular engineering of semi-transparent non-fullerene acceptors for quantum-enhanced agrivoltaics},
    pdfauthor={Teguia et al.},
    pdfsubject={Organic Photovoltaics, Quantum Energy Harvesting, Non-Markovian Dynamics},
    pdfkeywords={organic photovoltaics, non-fullerene acceptors, spectral engineering, quantum coherence, semi-transparent devices, agrivoltaics},
    colorlinks=true,
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue
}
% SIunitx configuration
\sisetup{
    locale = FR,
    detect-all = true,
    group-minimum-digits = 4,
    separate-uncertainty = true,
    multi-part-units = single,
    range-phrase = {--},
    range-units = single,
    number-unit-product = \,,
    input-comparators = { < > = \le \ge \ll \gg \leq \geq }
}

\DeclareSIUnit{\yr}{\text{yr}}
\DeclareSIUnit{\tonne}{\text{t}}
\DeclareSIUnit{\hectare}{\text{ha}}
\DeclareSIUnit{\kWh}{\text{kWh}}
\DeclareSIUnit{\hartree}{\text{E_h}}
\DeclareSIUnit{\bohr}{\text{a_0}}
\DeclareSIUnit{\USD}{\text{USD}}
%
\graphicspath{{Graphics/}}
%
%=============================================================================
% TITLE AND AUTHORS
%=============================================================================

\title{\textbf{Molecular engineering of semi-transparent non-fullerene acceptors for quantum-enhanced agrivoltaics}}

\author{
    Steve Cabrel Teguia Kouam$^{2,*}$,
    Theodore Goumai Vedekoi$^{1}$,
    Jean-Pierre Tchapet Njafa$^{1}$, \\
    Jean-Pierre Nguenang$^{2}$,
    Serge Guy Nana Engo$^{1}$ \\
    \\
    $^{1}$Department of Physics, Faculty of Science, University of Yaoundé I, Cameroon \\
    $^{2}$Department of Physics, Faculty of Science, University of Douala, Cameroon \\
    \\
    $^{*}$Corresponding author: \texttt{steve.teguia@facsciences-uy1.cm}
}

\date{\today}

%=============================================================================
% DOCUMENT BEGIN
%=============================================================================

\begin{document}

\maketitle

%=============================================================================
% ABSTRACT
%=============================================================================

\begin{abstract}
Semi-transparent organic photovoltaics (OPVs) based on non-fullerene acceptors (NFAs) have achieved power conversion efficiencies exceeding \SI{18}{\percent}, yet their potential for dual-use agrivoltaic applications remains limited by inefficient spectral matching with biological systems. Here, we demonstrate molecular engineering of PM6/Y6-BO derivatives that simultaneously deliver \SI{18.8}{\percent} PCE and quantum-enhanced photosynthetic energy transfer. By strategically tuning the spectral transmission to target vibronic resonances at \SIlist{750;820}{\nano\meter}, we extend excitonic coherence lifetimes by \SIrange{20}{50}{\percent} through non-Markovian dynamics, increasing the electron transport rate by \SI{25}{\percent} relative to Markovian baselines. The optimized donor-acceptor system exhibits balanced charge mobilities ($\mu_h/\mu_e \approx \SI{2e-3}{\centi\meter\squared\per\volt\per\second}$), suppressed non-geminate recombination ($k \leq \SI{1.2e-12}{\centi\meter\cubed\per\second}$), and operational stability exceeding \SI{18000}{\hour} (T$_{80}$). An AI-driven discovery pipeline screened \num{2847} candidates using equivariant graph neural networks, identifying configurations that maintain $>$\SI{80}{\percent} photosynthetic efficiency while achieving Pareto-optimal energy yields. Techno-economic analysis projects levelized costs of \SIrange{0.04}{0.06}{\USD\per\kWh} with revenue potential of \SIrange{470}{3000}{\USD\per\hectare\per\yr}. These findings establish quantitative design rules for co-optimizing photovoltaic performance and biological compatibility in next-generation semi-transparent OPV materials.
\end{abstract}

%=============================================================================
% KEYWORDS
%=============================================================================

\noindent\textbf{Keywords:} Organic photovoltaics, non-fullerene acceptors, spectral engineering, quantum coherence, semi-transparent devices, multi-objective optimization, AI-driven materials discovery, agrivoltaics

%=============================================================================
% MAIN CONTENT (MODULAR SECTIONS)
%=============================================================================

\input{files2/introduction}
\input{files2/theory_methods}
\input{files2/opv_materials}
\input{files2/results}
\input{files2/discussion}
\input{files2/conclusion}

%=============================================================================
% ACKNOWLEDGMENTS
%=============================================================================

\section*{Acknowledgments}

This work was supported by the University of Yaoundé I and the University of Douala.

%=============================================================================
% DATA AVAILABILITY
%=============================================================================

\section*{Data availability statement}

All data supporting the findings of this study are available within the article and its Supporting Information. Raw simulation output files, analysis scripts, and parameter sets are available from the corresponding author upon reasonable request. Our custom PT-HOPS/SBD simulation framework, computational notebooks, source code, and datasets generated during this study are available in the GitHub repository at \url{https://github.com/NanaEngo/Quantum_Agrivoltaic_HOPS}. Reproducibility information: All simulations were performed using Python 3.12.12, NumPy 2.0.2, and SciPy 1.14.1. Computational parameters and environment configurations are documented in the Supporting Information. All reported values include standard errors calculated from ensemble averaging, with \SI{95}{\percent} confidence intervals explicitly stated for all quantitative results derived from \num{100} independent realizations.

%=============================================================================
% CONFLICTS OF INTEREST
%=============================================================================

\section*{Conflicts of interest}

The authors declare no conflicts of interest.

%=============================================================================
% AUTHOR CONTRIBUTIONS
%=============================================================================

\section*{Author contributions}

\textbf{Steve Cabrel Teguia Kouam}: Methodology, validation, formal analysis, writing -- original draft. \textbf{Theodore Goumai Vedekoi}: Software, investigation, data curation, writing -- original draft. \textbf{Jean-Pierre Tchapet Njafa}: Conceptualization, theoretical framework, writing -- review \& editing. \textbf{Jean-Pierre Nguenang}: Resources, supervision, formal analysis. \textbf{Serge Guy Nana Engo}: Project administration, conceptualization, theoretical framework, final manuscript editing. All authors have given approval to the final version of the manuscript.

%=============================================================================
% REFERENCES
%=============================================================================

\bibliographystyle{wiley}
\bibliography{references}

%=============================================================================
% SUPPORTING INFORMATION
%=============================================================================

\section*{Supporting Information}

Supporting Information includes detailed OPV synthesis protocols, device fabrication procedures, quantum dynamics methods (PT-HOPS/SBD technical details), AI/ML model architecture specifications, stability testing protocols (ISOS standards), economic analysis details (LCOE calculations), and additional validation data (12 tests expanded).

%=============================================================================
\end{document}
%=============================================================================
